---
title: ' Random Forest Car Price '
output: pdf_document
---


```{r setup, include=FALSE }
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  fig.align = 'center'
  
)

library('caret')
library('rpart')
library ('rpart.plot')
library(dplyr)
library(ggplot2)
library(stringr)
library(randomForest)
library("party")
library(knitr)

```

### Read data set and clean data 
### Which variables are significant in predicting the price of a car?
### How well those variables describe the price of a car ?


```{r}




#Read data sets
car_data<-read.csv('Cars_Data.csv')
car_data2<-read.csv('Cars_Data.csv')

# Fix the car names
car_data$CarName<-gsub("maxda",'mazda',car_data$CarName)
car_data$CarName<-gsub("porcshce",'porsche',car_data$CarName)
car_data$CarName<-gsub("vokswagen",'volkswagen',car_data$CarName)
car_data$CarName<-gsub("vw",'volkswagen',car_data$CarName)
car_data$CarName<-gsub("toyouta",'toyota',car_data$CarName)
car_data$CarName<-gsub("Nissan",'nissan',car_data$CarName)

#add brand name column
brand<-car_data$CarName<-word(car_data$CarName,1)
car_data$brand<-brand

#How many cars of each brand?
car_count<-table (car_data$brand)
print(car_count)
car_count_df <- as.data.frame(car_count, check.names = FALSE)
names(car_count_df)[1]<-paste("Car_Brand")
names(car_count_df)[2]<-paste("Items")
car_count_df$Var1<-as.character(car_count_df$Car_Brand)

```

### Plot of the number of cars of each brand 
```{r}
ggplot(car_count_df,aes(x=Items,y=Car_Brand))+geom_point(aes(color= Car_Brand))+
scale_x_continuous(breaks = car_count_df$Items)
```

### Plot fuel type between all cars
```{r}
ggplot(car_data, aes(x = "", y = fueltype, fill = fueltype)) +
  geom_col() +coord_polar(theta = "y")
```

### Plot the distribution of cars and price 
```{r}
ggplot(car_data2,aes(x=car_ID,y=price,fill=price))+geom_smooth()
```

### Plot the distribution of car body and price 
```{r}
ggplot(car_data,aes(x=carbody,y=price,fill=carbody))+geom_boxplot()
```

### Plot the distribition of car body and price 
```{r}
ggplot(car_data,aes(x=enginetype,y=price,fill=enginetype))+geom_boxplot()
```

### Linear multivariate Model of price
```{r}

Car_Price_Regression<-lm(price~ symboling+fueltype+aspiration+doornumber+carbody+
                         drivewheel+enginelocation+enginelocation+wheelbase+carlength
                        +carwidth+carheight+curbweight+enginetype+cylindernumber+
                        enginesize+ fuelsystem+boreratio+stroke+compressionratio+
                        horsepower+compressionratio+peakrpm+citympg+highwaympg
                         ,data = car_data)

summary(Car_Price_Regression)
```

### Plot the biggest factor in car price
Horse power was the biggest positive factor according to our model
```{r}
ggplot(car_data,aes(x=horsepower,y=price))+geom_smooth()

```

### Random Forest Model
```{r}


#Delete variables for more predicted accuracy
car_data$car_ID<-NULL
car_data$symboling<-NULL
car_data$brand<-NULL


#test and training data cars data 
sample_data<-sample(c(TRUE,FALSE),nrow(car_data),replace=TRUE,prob =c(0.7,0.3))
train_data <- car_data[sample_data,]
test_data <- car_data[!sample_data,]

#Random forest model 
random_forest_model= randomForest(price~.,data = train_data)
print(random_forest_model)

#Predict using our test data with our trained model
predict_price= predict(random_forest_model,test_data,interval='prediction')

#add price predcition variable to test data data frame 
test_data$price_predict=predict_price
```

### The accuracy of the Random Forest Model
```{r}

#create data frame with price and predicted price 
show_prediction<-data.frame(test_data$price,test_data$price_predict)


#compare values 
all.equal(show_prediction$test_data.price,show_prediction$test_data.price_predict)
```

### plot the final results
```{r}
ggplot(show_prediction,                                    
       aes(x = test_data.price_predict,
           y = test_data.price
)) +
  geom_point() + geom_abline(color='red')


```


